%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

\namesection{Vishnu}{Sakthi Selvakumar}{}
{\small\contactline
  {\href{https://www.vishnusakthi.me}{Vishnusakthi.me}}
  {\href{https://github.com/vishnus1793}{vishnus1793}}
  {\href{https://www.linkedin.com/in/vishnu-s-0477ba246}{Vishnu S}}
  {\href{mailto:vishnusakthi.44@gmail.com}{vishnusakthi.44@gmail.com}}
  {\href{tel:+917397286386}{7397286386}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 

\section{Objective}

I want to grow my skills and contribute to a team that supports innovation, creativity, and practical problem-solving. I aim to work in an environment where I can learn, build real solutions, and add value to the organization.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{HOTEL BOOKING PLATFORM}
\descript{| \textsc{React, FastAPI, MongoDB, JWT, Docker}}
\\
\vspace{6pt}
\begin{tightemize}
\item Built full-stack booking system with role-based dashboards.
\item Developed REST APIs with JWT authentication and secure password hashing.
\item Implemented real-time availability checks preventing double bookings.
\item Optimized MongoDB queries using indexing (~35\% faster).
\item Deployed using Docker with environment-based configuration.
\end{tightemize}
\vspace{4pt}

\runsubsection{WEB SUMMARIZER WITH LOCAL LLM}
\descript{| \textsc{React, FastAPI, HuggingFace, BeautifulSoup}}
\\
\begin{tightemize}
\item Built full-stack app to scrape and summarize web content.
\item Designed asynchronous APIs reducing latency by ~30\%.
\item Integrated LSA, TextRank, and local BART for hybrid summarization.
\item Implemented caching and model preloading for faster inference.
\item Structured backend using modular architecture for scalability.
\end{tightemize}
\vspace{4pt}

\runsubsection{MULTI-SEARCH ENGINE SUMMARIZER}
\descript{| \textsc{Python, LLaMA3, Ollama, AsyncIO}}
\\
\begin{tightemize}
\item Integrated multiple search APIs with asynchronous processing.
\item Reduced redundant API calls by ~40\% using 24-hour caching.
\item Enabled offline summarization using local LLaMA3.
\item Implemented error handling and rate-limit management.
\item Designed clean service-layer architecture.
\end{tightemize}
\vspace{4pt}

\runsubsection{STOCK PRICE PREDICTION USING PYSPARK}
\descript{| \textsc{PySpark, MLlib, Time-Series Forecasting}}
\\
\begin{tightemize}
\item Built distributed pipeline for large-scale financial datasets.
\item Engineered time-series features for predictive modeling.
\item Implemented MLlib regression models for trend forecasting.
\item Optimized Spark transformations for improved execution speed.
\item Validated model performance using RMSE metrics.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}

\runsubsection{2ND PLACE – 30-HOUR HACKATHON}
\descript{| \textsc{KEC}}
\begin{tightemize}
\item Built full-stack room booking platform with 360° visualization.
\item Delivered functional prototype within 30 hours.
\item Collaborated in a 3-member team following rapid Agile workflow.
\end{tightemize}

\runsubsection{3RD PLACE – 24-HOUR HACKATHON}
\descript{| \textsc{KEC}}
\begin{tightemize}
\item Developed high-performance web scraping engine.
\item Structured and cleaned large-scale product data efficiently.
\item Optimized execution speed under strict 24-hour constraints.
\end{tightemize}

\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.25\textwidth} 

\section{Education} 

\subsection{Kongu Engineering College, Perundurai, Erode}
\descript{B.Tech in Artificial Intelligence and Machine Learning}
\location{2022 - 2026}
\location{CGPA: 7.30 / 10.0}
\sectionsep

\subsection{Kongu Vellalar Matric Higher Secondary School, Erode}
\descript{Higher Secondary Certificate (HSC)}
\location{79\%}
\sectionsep

\subsection{Nandha Matric Higher Secondary School, Erode}
\descript{Secondary School Leaving Certificate (SSLC)}
\location{69\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}

\textbf{Frontend:}\\
React.js, JavaScript (ES6+), HTML5, CSS3 \\[4pt]

\textbf{Backend:}\\
FastAPI, Node.js, Flask, REST APIs, JWT Authentication \\[4pt]

\textbf{Databases:}\\
MongoDB, SQL \\[4pt]

\textbf{DevOps \& Cloud:}\\
Docker, CI/CD, Terraform, AWS (EC2, S3), Linux \\[4pt]

\textbf{Programming:}\\
Python, JavaScript, Java, C \\[4pt]

\textbf{Tools:}\\
Git, GitHub, Postman

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}

\begin{itemize}
  \item GitHub Foundation
  \item MongoDB Associate Developer
  \item Docker Mastery: Kubernetes and Swarm
\end{itemize}

\end{minipage} 
\end{document}